---
title: "snapp_scicomp_issues"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(gh)
library(purrr)
library(tidyr)
library(curl)
library(keyring)
library(plotly)
library(rlang)
library(data.table)
library(DT)

```

# creating a new keyring that store git credentials

```{r}

# building off work done by Robert Saldivar

kb <- keyring::backend_file$new() #makes a new backend environment

# kb$keyring_create("Git_Credentials") #only run once, choose a password for your keyring when prompted

kb$keyring_unlock("Git_Credentials") #unlock so it's open to set values within keychain

kb$set(service = "Github_Enterprise_Token", username = "maggieklope", keyring = "Git_Credentials") #enter in personal authentication token (PAT) when prompted

# kb$get("Github_Enterprise_Token", keyring = "Git_Credentials") #run this if you need to view your PAT

kb$keyring_lock("Git_Credentials") #finish by locking keyring

```

# getting data from the SNAPP-wg-scicomp 

```{r}

issues_gh <- gh("/repos/SNAPP/snapp-wg-scicomp/issues", 
   .api_url = "https://github.nceas.ucsb.edu/api/v3", 
   owner = "SNAPP", 
   repo = "snapp-wg-scicomp",
   .token = kb$get("Github_Enterprise_Token", keyring = "Git_Credentials"),
   state = "all",
   .limit = "all")

```

# creating a data frame

```{r}

# getting number of issues to set row
n_issues <- 1:length(issues_gh)

# blank data frame
df_test <- data.frame()

# creating data frame
for (i in n_issues) {
  
 df_test <- rbind(df_test, data.frame(
   repo_num = i,
   title = issues_gh[[i]]$title, 
   creator = issues_gh[[i]]$user$login,
   assignees = ifelse(
      test = is.null(issues_gh[[i]]$assignee$login), # using ifelse() because rbind will remove NA, so would get error of not having enough rows
      yes = NA, 
      no = as.character(
         as.data.frame(issues_gh[[i]]$assignees) %>% 
         dplyr::select(contains("login")) %>% 
         unite(col = "assignees", sep = ", "))
      ),
   date_created = as.Date(issues_gh[[i]]$created_at), 
   status = issues_gh[[i]]$state,
   date_closed = ifelse(test = is.null(issues_gh[[i]]$closed_at), 
                        yes = NA, 
                        no = issues_gh[[i]]$closed_at) %>% as.Date(),
   labels = ifelse(
      test = length(issues_gh[[i]]$labels) == 0, 
      yes = NA, 
      no = as.character(
         flatten_dfc(issues_gh[[i]]$labels) %>% 
         dplyr::select(contains("name")) %>% 
         unite(col = "labels", sep = ", "))
      ),
   num_comments = issues_gh[[i]]$comments
   ))
 
}

write_csv(df_test, path = "df_test.csv")

```

# filtering by desired date
# currently only showing issues that were created and closed in 2020
```{r}

#enter desired dates in yyyy-mm-dd
start_date <- "2020-01-01"
end_date <- "2020-12-31"

df_filtered <- df_test %>% 
   dplyr::filter(date_created >= as.Date(start_date)) %>% 
   dplyr::filter(date_closed <= as.Date(end_date))

```


# using DT package

- datatable() creates a  HTML widget to display R data objects
- better way to sort dates might be to make a new column that has the name of the fiscal year (ex: 2019-2020) to sort with?

```{r}
 datatable(df_filtered
           # filter = 'top' # adds a filter to the top, works to restrict dates but is not very effective
           ) 

```

# function

Needs to include:
- backend environment for keyring (only needed when running on server?)
- name for keyring
- repo path
- repo url
- desired start and end dates


```{r}
function_test <- function(github_username, github_api_endpoint, url, repo_owner, repo_name){
  
  # makes a new backend environment
  kb <- keyring::backend_file$new() 
  
  # creates keyring
  kb$keyring_create("Git_Credentials")
  
  # unlocks keyring
  kb$keyring_unlock("Git_Credentials")
  
  # enter in personal authentication token (PAT) when prompted
  # to get PAT, go to github account > Settings > Developer Settings > Personal access tokens
  kb$set(service = "Github_Enterprise_Token", username = github_username, keyring = "Git_Credentials") 
  
  # finish by locking keyring
  kb$keyring_lock("Git_Credentials")
  
  # pulls the github issue
  issues_gh <- gh(github_api_endpoint, 
                  .api_url = url, 
                  owner = repo_owner, 
                  repo = repo_name,
                  .token = kb$get("Github_Enterprise_Token", keyring = "Git_Credentials"),
                  state = "all",
                  .limit = "all")
  
  # getting number of issues to set row
  n_issues <- 1:length(issues_gh)
  
  # blank data frame
  df_test <- data.frame()
  
  # creating data frame
  for (i in n_issues) {
    
    df_test <- rbind(df_test, data.frame(
      repo_num = i,
      title = issues_gh[[i]]$title, 
      creator = issues_gh[[i]]$user$login,
      assignees = ifelse(
        test = is.null(issues_gh[[i]]$assignee$login), # using ifelse() because rbind will remove NA, so would get error of not having enough rows
        yes = NA, 
        no = as.character(
          as.data.frame(issues_gh[[i]]$assignees) %>% 
            dplyr::select(contains("login")) %>% 
            unite(col = "assignees", sep = ", "))
      ),
      date_created = as.Date(issues_gh[[i]]$created_at), 
      status = issues_gh[[i]]$state,
      date_closed = ifelse(test = is.null(issues_gh[[i]]$closed_at), 
                           yes = NA, 
                           no = issues_gh[[i]]$closed_at) %>% as.Date(),
      labels = ifelse(
        test = length(issues_gh[[i]]$labels) == 0, 
        yes = NA, 
        no = as.character(
          flatten_dfc(issues_gh[[i]]$labels) %>% 
            dplyr::select(contains("name")) %>% 
            unite(col = "labels", sep = ", "))
      ),
      num_comments = issues_gh[[i]]$comments
    ))
    
  }
  
  
  
}

function_test(github_username = "maggieklope", 
              github_api_endpoint = "/repos/SNAPP/snapp-wg-scicomp/issues",
              url = "https://github.nceas.ucsb.edu/api/v3",
              repo_owner = "SNAPP",
              repo_name = "snapp-wg-scicomp")

```


